---
title: "dsx RNA-seq analysis"
author: "Sasha Mikheyev"
date: "2/16/2018"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, fig.path='figures/', fig.width=5, fig.height=5 )
```

```{r libraries, message = FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(sleuth)   # gene expression
library(edgeR)    # gene expression
library(qvalue)   # multiple comparisons
library(ggsignif) # significance boxplots
library(scatterD3)# interactive scatterplots
library(networkD3)# interactive networks
library(GOstats)  # GO terms
library(GSEABase) # GO terms
library(devtools) #better session info
library(WGCNA)    # gene co-expression
allowWGCNAThreads()
```

## QC using RSEM data
```{r qc, message = FALSE} 
counts <- read_csv("data/genes_counts.csv")
tpm <- read_csv("data/genes_tpm.csv")
treatments <- read_csv("data/treatments.csv", col_types = "ccc")
ercc <- left_join(read_tsv("data/ercc.tsv"), tpm, by = "gene_id") 
descriptions <- read_tsv("data/descriptions.tsv", col_names = c("gene_id", "description"))
mix1 <-  ercc[,c("gene_id", "mix1", subset(treatments, spikein == "mix1")$sample)] %>% gather( library, observed, -c(mix1,gene_id)) %>% dplyr::rename(expected = mix1 )
mix2 <- ercc[,c("gene_id", "mix2", as.character(subset(treatments, spikein == "mix2")$sample))] %>% gather( library, observed, -mix2, -gene_id) %>% dplyr::rename(expected = mix2 )
ercc <- rbind(mix1,mix2)
ggplot(ercc, aes(observed+1, expected+1, color=as.factor(library))) + geom_point() + scale_y_continuous(trans='log2')+scale_x_continuous(trans='log2')+ geom_abline()+guides(color=F)

cutoff <- seq(0,5,by=0.1)
r <- c()
for (i in cutoff) {
  keepGenes <- ercc %>% group_by(gene_id, library) %>% summarise(all_mean = mean(observed)) %>% filter(all_mean > i) %>% .$gene_id %>% unique
  r <- c(r, summary(lm(log2(observed+1)~log2(expected+1), data=subset(ercc, gene_id %in% keepGenes)))$r.squared)
}
plot(cutoff,r)
```

The signal to noise is basically fine even at the lowest levels, so we do not do any abundance-based filtering.

## Gene expression analysis {.tabset .tabset-fade}

The data are fairly noisy, so we conducted the DGE analysis using two separate alignment/counting philosophies. The more tradional approach uses alignment-based gene quantification using RSEM, and the second one uses a kmer-based approach implemented in Kallisto. Each analysis is shown in a separate tab.

### RSEM/EdgeR analysis

```{r edgeR}
counts <- counts %>% filter(! grepl("ERCC", gene_id))
design <- model.matrix(~treatment, treatments)
cds <- DGEList( counts[,  treatments$sample] , group = treatments$treatment)
dim(cds)
cds <- calcNormFactors( cds) 
plotMDS( cds)
cds <- estimateDisp( cds, design)
de.tgw <- exactTest( cds , pair = c( "DSX" , "GFP" ) )
de.tgw$table$gene_id <- counts$gene_id
de.tgw$table <- left_join(de.tgw$table, descriptions, by = "gene_id") 
de.tgw$table %>% filter(gene_id  == "Dsx")
de.tgw$table %>% filter(gene_id  == "Vg")
de.tgw$table %>% filter(gene_id  == "Mrjp1")
de.tgw$table %>% filter(gene_id  == "Dnmt3")

dsxTest <- function(a,b) return(data.frame(p.value = de.tgw$table %>% filter(gene_id  == "Dsx") %>% .$PValue))
data.frame(tpm = t(subset(tpm, gene_id == "Dsx")[,as.character(treatments$sample)]) , trt = treatments$treatment) %>% ggplot(aes(trt,tpm))+geom_boxplot() + geom_signif(comparisons = list(c("DSX", "GFP")), test = "dsxTest") + xlab("dsRNA injected")+ylab("TPM")

vgTest <- function(a,b) return(data.frame(p.value = de.tgw$table %>% filter(gene_id  == "Vg") %>% .$PValue))
data.frame(tpm = t(subset(tpm, gene_id == "Vg")[,as.character(treatments$sample)]) , trt = treatments$treatment) %>% ggplot(aes(trt,tpm))+geom_boxplot() + geom_signif(comparisons = list(c("DSX", "GFP")), test = "vgTest") + xlab("dsRNA injected")+ylab("TPM")
```

#### Isoform-specific expression using EdgeR

We are using single-end reads, so we don't expect much power to distinguish isoforms, but is is worth checking.

```{r rsemIsoforms}
dsxIsoforms <- tibble(isoform_id = c("NM_001111255.1", "NM_001134935.1", "NM_001134936.1", "NR_024131.1" ,"XM_006560013.2"), description = c("M", "F2", "B", "RNA", "X1"))
isoforms <- read_csv("data/isoforms.csv") %>% filter(! grepl("ERCC", isoform_id))
cdsIso <- DGEList( isoforms[, treatments$sample], group = treatments$treatment)
cdsIso <- calcNormFactors( cdsIso) 
cdsIso <- estimateDisp( cdsIso, design)
deIso.tgw <- exactTest( cdsIso , pair = c( "DSX" , "GFP" ) )
deIso.tgw$table$isoform_id <- isoforms$isoform_id
kable(deIso.tgw$table %>% filter(isoform_id %in% dsxIsoforms$isoform_id) %>% left_join(dsxIsoforms, by = "isoform_id"))
```

Actually, the X1 isoform, the one we actually knocked down is significantly lower in the _Dsx_ RNAi-treated bees (using a one-tailed test).

### Kallisto/Sleuth analysis

```{r kallistoSleuthTable, eval = F}
treatments <- treatments %>% mutate(path = paste0("./data/kallisto/", sample))
t2g <- read_tsv("data/g2i.tsv", col_names=c('target_id','gene_id', 'description'))
so <- sleuth_prep(treatments, target_mapping = t2g, aggregation_column = 'gene_id')
so <- sleuth_fit(so, ~treatment, 'full')
so <- sleuth_fit(so, ~1, 'reduced')
so <- sleuth_lrt(so, 'reduced', 'full')
sleuth_table <- sleuth_results(so, 'reduced:full', 'lrt', show_all = FALSE)
saveRDS(sleuth_table, "data/sleuth_table.rds")
```

```{r kallistoSleuthTableLoad, echo = FALSE}
sleuth_table <- readRDS("data/sleuth_table.rds")
```

```{r kallistoDsx}
sleuth_table %>% filter(target_id == "Dsx")
```

Both quantification approaches provide the same result, _Dsx_ is upregulated in the control bees, and so is _Vg_ (as predicted).

## Weighted gene co-expression analysis

We are interested in understanding the netwoks of genes co-expressed with _Dsx_ in honey bees, and to checke whether this network is associated with RNAi treatment. 

```{r pickSoftThreshold, warning=FALSE}
expDat <- as.data.frame(t(tpm %>% filter(! grepl("ERCC", gene_id)) %>% dplyr::select(-gene_id)))
colnames(expDat) <- tpm %>% filter(! grepl("ERCC", gene_id)) %>% .$gene_id
expDat <- expDat[as.character(treatments$sample),] # re-arrange to match treatments vector
pickSoftThreshold(expDat, RsquaredCut = 0.8, networkType = "unsigned")$powerEstimate
SoftPower = 12
```

We'll pick soft power 12, which is over the 0.8 threshold.

```{r wgcna, eval = F}
net <- blockwiseModules(expDat, power = SoftPower,
TOMType = "unsigned", minModuleSize = 30,
reassignThreshold = 0, mergeCutHeight = 0.25,
numericLabels = TRUE, pamRespectsDendro = FALSE,
saveTOMs = FALSE,
verbose = 3, maxBlockSize = 15000)
saveRDS(net, "data/net.rds")
```

```{r loadNet, echo = FALSE}
# load pre-computed network results to save time
net <- readRDS("data/net.rds")
```

```{r modleTrait}
MEs0 <- moduleEigengenes(expDat, net$colors)$eigengenes
MEs <- orderMEs(MEs0)
modNames <- substring(names(MEs), 3)
moduleTraitCor <- cor(MEs, as.numeric(gsub("GFP",0,gsub("DSX",1,treatments$treatment))), method = "spearman");
moduleTraitPvalue <- corPvalueStudent(moduleTraitCor, 20)
(DsxModule <- net$colors[which(colnames(expDat) == "Dsx")])
table(net$colors) %>% kable("html", caption = "Number of genes in the different modules. The Dsx-repsonsive module is highlighted", col.names
 = c("Module", "Number of genes")) %>% kable_styling() %>% row_spec(DsxModule+1, background = "red") %>% scroll_box(height = "200px") 
```

### Exploring the _Dsx_-containing module

####  Intramodular connectivity and gene significance

```{r connectivity}
Alldegrees <- intramodularConnectivity.fromExpr(expDat, net$colors, power = SoftPower)
rownames(Alldegrees) <- colnames(expDat)
geneModuleMembership <- as.data.frame(cor(expDat, MEs, use = "p"));
Alldegrees["Dsx",]
DsxModuleGenes <- colnames(expDat)[net$colors == DsxModule]
connectivityDsxModule <- data.frame(kWithin = Alldegrees[DsxModuleGenes,"kWithin"], gene_id = rownames(Alldegrees[DsxModuleGenes,]), moduleMembership = geneModuleMembership[DsxModuleGenes, paste0("ME",DsxModule)]) %>% left_join(de.tgw$table, by = "gene_id")
```

```{r dsxModuleGenes}
dsxModuleGenes <- descriptions %>% filter(gene_id %in% colnames(expDat)[net$colors == DsxModule] ) %>% left_join(de.tgw$table, by = "gene_id") %>% left_join(connectivityDsxModule %>% dplyr::select(gene_id, kWithin), by="gene_id") %>% dplyr::select(gene = gene_id, description = description.x, logFC, kWithin, logCPM) %>% arrange(desc(logFC))  
highligh <- which(dsxModuleGenes$gene %in% c("Vg", "Dsx", "Dnmt3"))
```
##### Table S1. Genes in the _Dsx_-responsive module{.tabset .tabset-fade}

In addition to _Dsx_, this module contains _Vg_, as predicted. It also contains the DNA methyltransferase _Dnmt3_, which has been shown to be involved in queen/worker differentiation during development.

###### Sorted by logFC 
```{r dsxTable, echo=F}
dsxModuleGenes  %>% kable(format = "html", caption = "Genes in the Dsx-containing module. Higher values of logFC correspond to greater expression in control bees. Genes known to be assciated with reproductive division of labor are highlighted in red.") %>% row_spec(highligh, bold = T, color = "white", background = "#D7261E") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(height = "400px") 
```

###### Sorted by intra-modular connectivity
```{r dsxTableConnectivity, echo=F}
dsxModuleGenes  %>% arrange(desc(kWithin)) %>% kable(format = "html", caption = "Genes in the Dsx-containing module. Higher values of logFC correspond to greater expression in control bees. Genes known to be assciated with reproductive division of labor are highlighted in red.") %>% row_spec(highligh, bold = T, color = "white", background = "#D7261E") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(height = "400px") 
```


```{r connectivityTest}
with(connectivityDsxModule, cor.test(logFC, kWithin, method = "s"))
interestingGenes <- c("Dsx", "Vg")
p <-ggplot(connectivityDsxModule, aes(logFC, kWithin))+geom_point(alpha=0.1) +geom_point(data=subset(connectivityDsxModule, gene_id %in% interestingGenes), colour="red")+theme_bw()+geom_text(data=subset(connectivityDsxModule, gene_id %in% interestingGenes), aes(label = gene_id), nudge_x=.2)+stat_smooth(method="lm", color="blue", se = F)
ggsave("Dsx module.pdf", width = 5, height = 5)
```

##### Figure S1. Module membership _vs._ treatment effect
Hover over the points to reveal gene names. There is a significant correlation between connectivity within this module and log-fold change as a result of RNAi treatment. In other words, this is a _Dsx_-responsive module.

```{r conectivityFigure, echo = F}
connectivityDsxModule$interesting <- .2
connectivityDsxModule$interestingLabes <- "" 
connectivityDsxModule[connectivityDsxModule$gene_id %in% c("Dsx", "Vg"),"interesting"] <- 1
connectivityDsxModule[connectivityDsxModule$gene_id == "Vg","interestingLabes"] <- "Vg"
connectivityDsxModule[connectivityDsxModule$gene_id == "Dsx","interestingLabes"] <- "Dsx"

with(connectivityDsxModule, scatterD3(x = logFC, y = kWithin, size_var = interesting, size_range = c(30,100), hover_size = 4, hover_opacity = 1, opacity_var = interesting, col_var = interesting , lab = interestingLabes, tooltip_text = description, legend_width = 0, xlim=c(-1,3), ylim=c(0,100), xlab = "Log2 fold-count", ylab = "Witin-module connectivity"))
```

#### GO term enrichment

```{r go, warning = FALSE}
go <- read_tsv("data/go.tsv", col_types = cols()) %>% mutate(evidence = "ISS") %>% dplyr::select(GO=go, evidence,gene=gene_id)
universe <- unique(go$gene)
goFrame <- GOFrame(as.data.frame(go %>% dplyr::filter(gene %in% universe)), organism="Apis melliefera")
goAllFrame <- GOAllFrame(goFrame)
gsc <- GeneSetCollection(goAllFrame, setType = GOCollection())

DsxModuleGo <- hyperGTest(GSEAGOHyperGParams(name = "enriched in Dsx module",
    geneSetCollection=gsc,geneIds = intersect(dsxModuleGenes$gene,universe), universeGeneIds=universe, ontology = "BP",pvalueCutoff = 0.05,conditional = FALSE,testDirection = "over"))
```

###### Table S2. GO term enrichmed in _Dsx_-responsive module

```{r goTable}
summary(DsxModuleGo) %>% kable("html", digits = 3) %>% kable_styling() %>%  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = T) %>% scroll_box(height = "400px") 
```

Virtually all the GO terms enriched in the _Dsx_-responsive module have to do with regulation, and it is full of transcription factors and other regulatory genes. This is expected, given that _Dsx_ is a master regulatory gene.

#### Visualizing genes connected to Dsx.
```{r networkPlotPrep, eval = F}
maxTopGenes <- 30
DsxConnections <- data.frame(cor = cor(expDat[,net$colors == DsxModule], expDat[, "Dsx"]), annot = descriptions$description[match(colnames(expDat[,net$colors == DsxModule]), descriptions$gene_id)])
topGenes <- rownames(DsxConnections)[order(DsxConnections$cor, decreasing = T)[1:maxTopGenes]]
ADJ <- abs(cor(expDat, use="p"))^SoftPower
TOM  <- TOMsimilarity(ADJ)
modTOM <- TOM[net$colors == DsxModule, net$colors == DsxModule]
dimnames(modTOM) = list(DsxModuleGenes, DsxModuleGenes)
saveRDS(modTOM, "data/modTOM.rds")
```

```{r loadTOM, echo = FALSE}
maxTopGenes <- 30
DsxConnections <- data.frame(cor = cor(expDat[,net$colors == DsxModule], expDat[, "Dsx"]), annot = descriptions$description[match(colnames(expDat[,net$colors == DsxModule]), descriptions$gene_id)])
topGenes <- rownames(DsxConnections)[order(DsxConnections$cor, decreasing = T)[1:maxTopGenes]]
modTOM <- readRDS("data/modTOM.rds")
```

##### Figure S2. Interactive network of _Dsx_-connected genes
This network shows the 30 genes most highly connected to _Dsx, with edge weights proportional to the strength of the connection, and node areas to log counts per million.
```{r networkPlot, echo = FALSE}
edges <- data.frame(source = c(), target = c(), value = c())
for (i in 1:maxTopGenes)
  for (j in i:maxTopGenes)
    if (modTOM[i,j]>.07 & i != j) edges <- rbind(edges, data.frame(source = i-1, target = j-1, value = modTOM[i,j]))
edges$value <- edges$value/max(edges$value)*3

nodes <- data.frame(name = rownames(DsxConnections[topGenes,]), description = DsxConnections[topGenes,"annot"], color = c(c("red"),rep("grey", maxTopGenes - 1)), logCPM = de.tgw$table[match(topGenes,de.tgw$table$gene_id),"logCPM"])
forceNetwork(Links = edges, Nodes = nodes,
            Source = "source", Target = "target",
            Value = "value", NodeID = "description",  fontSize = 18, linkDistance = 150, linkWidth =  JS("function(d) { return d.value; }"),colourScale = JS("d3.scaleOrdinal(d3.schemeCategory20);"), Nodesize = "logCPM", radiusCalculation = JS("d.nodesize+3"), fontFamily = "arial", Group = "color", opacity = 0.8, width = 500, height = 500)
```

## Comparisons with other studies

### A comparison of honeybee (_Apis mellifera_) queen, worker and drone larvae by RNA-Seq ([He et al. 2017](http://onlinelibrary.wiley.com/doi/10.1111/1744-7917.12557/full/))

This is a well-replicated data set on early development across castes. They did not find _dsx_ differential expression when they looked at their data.

```{r heDGE}
heCounts <- read_csv("data/he_genes_counts.csv.gz", col_types = cols()) %>% filter(! grepl("ERCC", gene_id))
heTPM <- read_csv("data/he_tpm.csv.gz", col_types = cols()) %>% filter(! grepl("ERCC", gene_id))
heFactors <- read_tsv("data/he_factors.tsv", col_types = cols()) %>% filter(sex == "female")
design <- model.matrix(~caste, heFactors)
cdsHe <- DGEList( heCounts[,  heFactors$sample] , group = heFactors$caste)
cdsHe <- calcNormFactors( cdsHe) 
mdsPlot <- plotMDS( cdsHe, labels = paste(heFactors$caste, "_", heFactors$age))
cdsHe <- estimateDisp( cdsHe, design)
deHe.tgw <- exactTest( cdsHe , pair = c( "worker" , "queen" ) )
deHe.tgw$table$gene_id <- heCounts$gene_id
deHe.tgw$table <- left_join(deHe.tgw$table, descriptions, by = "gene_id") 

# positive logFC means upregulated in the worker
deHe.tgw$table %>% filter(gene_id  == "Dsx")
deHe.tgw$table %>% filter(gene_id  == "Vg")
deHe.tgw$table %>% filter(gene_id  == "Mrjp1")
deHe.tgw$table %>% filter(gene_id  == "Dnmt3")

data.frame(tpm = t(as.vector(heTPM %>% dplyr::filter(gene_id == "Mrjp1") %>% dplyr::select(heFactors$sample))), caste = heFactors$caste) %>% ggplot(aes(caste,tpm))+geom_boxplot()+ggtitle("Mrjp1")
data.frame(tpm = t(as.vector(heTPM %>% dplyr::filter(gene_id == "Vg") %>% dplyr::select(heFactors$sample))), caste = heFactors$caste) %>% ggplot(aes(caste,tpm))+geom_boxplot()+ggtitle("Vg")
```
The MDS plot is really nice, you can see how the castes start slighly different and then become progressively more so. As reported by He _et al._ there is no differential expression in the 

```{r heIsoforms}
dsxIsoforms <- tibble(isoform_id = c("NM_001111255.1", "NM_001134935.1", "NM_001134936.1", "NR_024131.1" ,"XM_006560013.2"), description = c("M", "F2", "B", "RNA", "X1"))
heIsoforms <- read_csv("data/he_isoforms_counts.csv.gz", col_types = cols()) %>% filter(! grepl("ERCC", isoform_id))
heCdsIso <- DGEList( heIsoforms[, heFactors$sample], group = heFactors$caste)
heCdsIso <- calcNormFactors( heCdsIso) 
heCdsIso <- estimateDisp( heCdsIso, design)
heCdsIso.tgw <- exactTest( heCdsIso , pair = c( "worker" , "queen" ) )
heCdsIso.tgw$table$isoform_id <- heIsoforms$isoform_id
kable(heCdsIso.tgw$table %>% filter(isoform_id %in% dsxIsoforms$isoform_id) %>% left_join(dsxIsoforms, by = "isoform_id"))
```

As reported by the authors, _Dsx_ is not differentially expressed by caste. However, even in our experiment, the difference is marginal, so we should look in some greater detail at other associated genes.

```{r hePickSoftThreshold, warning=FALSE}
heExpDat <- as.data.frame(t(heTPM[,-1]))
colnames(heExpDat) <- heTPM$gene_id
pickSoftThreshold(heExpDat, RsquaredCut = 0.8, networkType = "unsigned")$powerEstimate
```

It is pretty close to what we have in the other network, and we'll use the same power 12

```{r heWGNCA, eval = FALSE}
heNet <- blockwiseModules(heExpDat, power = 12,
TOMType = "unsigned", minModuleSize = 30,
reassignThreshold = 0, mergeCutHeight = 0.25,
numericLabels = TRUE, pamRespectsDendro = FALSE,
saveTOMs = FALSE,
verbose = 3, maxBlockSize = 15000)
saveRDS(heNet, "data/he_net.rds")
```

```{r heWGNCAload, echo =F}
heNet <- readRDS("data/he_net.rds")
```

Do the _Dsx_ containing modules overlap between studies
```{r modulePhyper}
heAlldegrees <- intramodularConnectivity.fromExpr(heExpDat, heNet$colors, power = 12)
heAlldegrees$gene_id <- colnames(heExpDat)
(heDsxModule <- heNet$colors[which(colnames(heExpDat) == "Dsx")])
heDsxModuleGenes <- colnames(heExpDat)[heNet$colors == heDsxModule]

bothDsx <- table(net$colors == DsxModule & heNet$colors == heDsxModule)[2]
heDsx <- table(heNet$colors == heDsxModule)[2]
ourDsx <- table(net$colors == DsxModule)[2]
phyper(bothDsx, ourDsx, table(net$colors == DsxModule)[1], heDsx, lower.tail = F)
sum(bothDsx)/sum(ourDsx)

heDsxModuleGenes <- descriptions %>% filter(gene_id %in% colnames(heExpDat)[heNet$colors == heDsxModule] ) %>% left_join(deHe.tgw$table, by = "gene_id") %>% left_join(heAlldegrees %>% dplyr::select(gene_id, kWithin), by="gene_id") %>% dplyr::select(gene = gene_id, description = description.x, logFC, kWithin, logCPM) %>% arrange(desc(logFC))  
highligh <- which(heDsxModuleGenes$gene %in% colnames(heExpDat)[net$colors == DsxModule])
heDsxModuleGenes  %>% arrange(desc(kWithin)) %>% kable(format = "html", caption = "Genes in the Dsx-containing module from He et al. Higher values of logFC correspond to greater expression in queens Genes also found in the Dsx-responsive module from the RNAi experiment are highlighted in yellow") %>% row_spec(highligh, bold = T, background = "#FFFF00") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(height = "400px") 
```

Yes, roughly half of the genes in the _Dsx_-responsive module form the RNAi experiment are found in the _Dsx_-containing module determined from larval gene expression.

Now, is the _Dsx_-containig module associated with caste-biased gene expression?

```{r casteBias}
# module membership vs logFC
cor.test(heAlldegrees$kWithin[net$colors == heDsxModule], deHe.tgw$table$logFC[net$colors == heDsxModule], method = "s")

#logFC in experimental vs developmental modules
with(left_join(deHe.tgw$table[heNet$colors == heDsxModule,],de.tgw$table[net$colors == DsxModule,] %>% dplyr::select(gene_id, logFC), by = "gene_id") %>% na.omit(), cor.test(logFC.x, logFC.y, method="s"))
```

This means that the _Dsx_-containing module is associated with queen-upregulated genes during development. The number of genes that overlap in the two modules is not very large, but their logFC are (negatively) correlated.

```{r echo=F, eval=F}
# Sanity checking to make sure the log-fold orintation makes sense
data.frame(tpm = t(as.vector(heTPM %>% dplyr::filter(gene_id == "Or30") %>% dplyr::select(heFactors$sample))), caste = heFactors$caste) %>% ggplot(aes(caste,tpm))+geom_boxplot()+ggtitle("Or30") # strongly positve log-fold gene

data.frame(tpm = t(as.vector(heTPM %>% dplyr::filter(gene_id == "LOC410743") %>% dplyr::select(heFactors$sample))), caste = heFactors$caste) %>% ggplot(aes(caste,tpm))+geom_boxplot()+ggtitle("LOC410743") # strongly negative log-fold gene

#yep, queens have positive log-fold changes. This is lined up with the experimental log-fold, where control bees were expected to be more queen-like in ovarian development.
```


## Session info
```{r sessioninfo, echo=F}
sessionInfo <- devtools::session_info() 
sessionInfo$platform 
sessionInfo$packages %>% kable("html") %>% kable_styling() %>% scroll_box(height = "400px") 
```
